---
title: "GH_2gen_2021"
author: "Mohammad Inam Jameel"
date: "4/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r, include = FALSE}
#Setting up the environment (not printed)
#libraries
library(dplyr)
library(ggplot2)
library(nlme)
library(lme4)
packageVersion("lme4")
library(tidyr)
library(broom)
library(car)
library(MASS)
library(emmeans)
library(visreg)
library(fitdistrplus)
library(gamlss)
library(rjags)
library(gamlss)
library(effects)

 
setwd("~/Desktop/Anderson_data/herbivory/data/greenhouse/")


#read in data 
gh2 <- read.csv("~/Desktop/Anderson_data/herbivory/data/greenhouse/gen2_GHSummary2022.csv")

gh2 <- filter(gh2, Include == "yes" )

#gh2 <- drop_na(gh2,LAR)
gh2 $S_elev<-scale(gh2$elevation,center=TRUE, scale=TRUE)
gh2$elev<-gh2$elevation/1000
gh2 $S_init_size<-scale(gh2$ini_size,center=TRUE, scale=TRUE)



# convert LAR from census 3 (most damage) and census 13 (most recent) to proportion
 gh2$LAR_prop2<- gh2$S2_LAR2/100
  hist(gh2$LAR_prop2)  

##Some of your variables are being read as characters not factors. Let's fix that
gh2$genotype<-as.factor(gh2$genotype)
gh2$treatment<-as.factor(gh2$treatment)
gh2$block<-as.factor(gh2$block)
gh2$mat_treat<-as.factor(gh2$mat_treat)
gh2$mat_exp_ID <-as.factor(gh2$mat_exp_ID) #need to include this as random effect since multiple reps per mat line
#gh2$trichomes <- gh2$avg_trichomes +0.001 #added to do gamma glmer
```
## Relative contributions {.tabset}

### SLA individual for full dataset
```{r}
#SLA for second season is S2_SLA
#also have to filter for the indiv that we have appropriate values for SLA (filter(gh2,S2_include_SLA = 1)

RC_SLA<- lmer(S2_SLA ~ treatment*elev*mat_treat+S_init_size +(1|block),control = lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e7)), test)
Anova(RC_SLA)
plot (RC_SLA)

visreg(RC_SLA, overlay = TRUE, "elev", by="treatment", type="conditional", scale = "response", 
       xlab="Elevation (m)", ylab="Specific leaf area", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
       fill=list(col=grey(c(0.7,0.9))),
       line=list(col=grey(c(0,0.5))),
       points=list(cex=1.5,col=grey(c(0.2,0.8))))  

visreg(RC_SLA,overlay = TRUE, "elev", by="mat_treat",type="conditional", scale = "response", 
       xlab="Elevation (m)", ylab="Specific leaf area", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
      #fill=list(col=grey(c(0.7,0.9))),
      #line=list(col=grey(c(0,0.5))),
       #points=list(cex=1.5,col=grey(c(0.2,0.8)))
      )  


```


```{r eval = FALSE, echo = FALSE} 
#### SLA individual for Parents. Save for later?

#p_SLA <- subset(test, mat_treat == "Parent")

#parents_SLA<- lmer(S2_SLA ~ treatment * elev + (1|block) + (1|genotype),control = lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e7)), data = p_SLA)
Anova(parents_SLA)
plot (parents_SLA)

visreg(parents_SLA, overlay = TRUE, "elev", by="treatment", type="conditional", scale = "response", 
       xlab="Elevation (m)", ylab="Specific leaf area", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
       fill=list(col=grey(c(0.7,0.9))),
       line=list(col=grey(c(0,0.5))),
       points=list(cex=1.5,col=grey(c(0.2,0.8))))  

library(rstatix)

#descriptive and visual look at variable
parents1 <- p_SLA %>% 
  group_by(treatment) %>%
  get_summary_stats(S2_SLA, type="mean_se")
parents1

```


### SLA family level

```{r eval = FALSE, echo = FALSE}
#not printed

#to make the emmeans file
modB<- lmer(SLA100 ~ genotype*mat_treat*treatment+S_init_size +(1|block),control = lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e7)), data = gh2)
fam_avg_linear<-emmeans(modB, ~genotype:mat_treat:treatment)
fam_means_linear<-as.data.frame(fam_avg_linear)
write.csv(fam_means_linear,file="LSmeans_SLA_2.csv")

#read in emmeans
LSmeans_SLA <- read.csv("LSmeans_SLA_2.csv", stringsAsFactors=TRUE)

#now we have lsmeans, but need to add corresponding elevation
elev <- gh2[c("genotype","elevation")] #make dataframe of genotypes and corresponding elev
elev <- unique(elev) #calls unique rows 
LSmeans_SLA <- merge(LSmeans_SLA,elev,by="genotype") #merge the dataframes

LSmeans_SLA$elev<-LSmeans_SLA$elevation/1000
#LSmeans_SLA$emmean<-LSmeans_SLA$emmean*100

write.csv(LSmeans_SLA,file="LSmeans_SLA_2.csv")

```

```{r}
#read in emmeans
LSmeans_SLA <- read.csv("LSmeans_SLA_2.csv", stringsAsFactors=TRUE)

RC_SLA_means<- lm(emmean ~ elevation*treatment*mat_treat, data = LSmeans_SLA)
Anova(RC_SLA_means)
plot(RC_SLA_means)

##use this

visreg(RC_SLA_means, overlay = TRUE, "elevation", by="treatment", type="conditional", scale = "response", 
       xlab="Elevation (m)", ylab="specific leaf area", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
       fill=list(col=grey(c(0.7,0.9))),
       line=list(col=grey(c(0,0.5))),
       points=list(cex=1.5,col=grey(c(0.2,0.8))))  

visreg(RC_SLA_means, overlay = FALSE, "elevation", by="mat_treat", type="conditional", scale = "response", 
       xlab="Elevation (m)", ylab="specific leaf area", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
       #fill=list(col=grey(c(0.7,0.9))),
       #line=list(col=grey(c(0,0.5))),
       #points=list(cex=1.5,col=grey(c(0.2,0.8)))
       ) 

```



### Trichomes individual

```{r}
RC_Tri<- glmer(trichomes ~ mat_treat*elev*treatment+S_init_size +(1|block),family = Gamma(link=log), data = gh2) 
#had errors but this seems to work when i specify link=log
#singular fit

Anova(RC_Tri) # elev is sig, sig interaction btw mat_treat and elev
plot (RC_Tri)

visreg(RC_Tri, "elev", by="treatment",overlay = TRUE,type="conditional", scale = "response", 
       xlab="Elevation (m)", ylab="Trichome density", partial=FALSE, cex.lab = 1.5,cex.axis = 1.5,
       fill=list(col=grey(c(0.7,0.9))),
       line=list(col=grey(c(0,0.5))),
       points=list(cex=1.5,col=grey(c(0.2,0.8))))  

visreg(RC_Tri, "elev", type="conditional", scale = "response", 
       xlab="Elevation (m)", ylab="Trichome density", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
       fill=list(col=grey(c(0.7,0.9))),
       line=list(col=grey(c(0,0.5))),
       points=list(cex=1.5,col=grey(c(0.2,0.8))))  



visreg(RC_Tri, "elev",  by="mat_treat", type="conditional", scale = "response", 
       xlab="Elevation (m)", ylab="Trichome density", partial=FALSE, cex.lab = 1.5,cex.axis = 1.5,
       fill=list(col=grey(c(0.7,0.9))),
       line=list(col=grey(c(0,0.5))),
       points=list(cex=1.5,col=grey(c(0.2,0.8))))  

visreg(RC_Tri, "elev",  by="mat_treat", type="conditional", scale = "response", 
       xlab="Elevation (m)", ylab="รง", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
       fill=list(col=grey(c(0.7,0.9))),
       line=list(col=grey(c(0,0.5))),
       points=list(cex=1.5,col=grey(c(0.2,0.8))))  


```

### Trichomes family level

```{r eval = FALSE, echo = FALSE}
# not printed
#to make the emmeans file
# link log makes log output ( i think), changed to identity but have some warnings. needs the glmer control
modC<- glmer(trichomes ~ mat_treat*genotype*treatment+(1|block),family = Gamma(link="identity"),  control=glmerControl(optimizer="bobyqa"), data = gh2) #s_initial size not sig, so not included
Anova(modC)
fam_avg_linear<-emmeans(modC, ~genotype:mat_treat:treatment)
fam_means_linear<-as.data.frame(fam_avg_linear)
write.csv(fam_means_linear,file="LSmeans_tri.csv")

#read in emmeans
LSmeans_tri <- read.csv("LSmeans_tri.csv", stringsAsFactors=TRUE)

#now we have lsmeans, but need to add corresponding elevation
elev <- gh2[c("genotype","elevation")] #make dataframe of genotypes and corresponding elev
elev <- unique(elev) #calls unique rows 
LSmeans_tri <- merge(LSmeans_tri,elev,by="genotype") #merge the dataframes

LSmeans_tri$elev<-LSmeans_tri$elevation/1000

write.csv(LSmeans_tri,file="LSmeans_tri.csv")
```

```{r}
LSmeans_tri <- read.csv("LSmeans_tri.csv", stringsAsFactors=TRUE)

RC_tri_means<- glm(emmean ~ mat_treat*elev*treatment, data = LSmeans_tri) 
Anova(RC_tri_means)
plot(RC_tri_means)



##use this

visreg(RC_tri_means, overlay = TRUE, "elev", by="treatment", type="conditional", scale = "response", 
       xlab="Elevation (m)", ylab="Trichome density", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
       fill=list(col=grey(c(0.7,0.9))),
       line=list(col=grey(c(0,0.5))),
       points=list(cex=1.5,col=grey(c(0.2,0.8))))  

visreg(RC_tri_means, overlay = FALSE, "elev", by="mat_treat", type="conditional", scale = "response", 
       xlab="Elevation (m)", ylab="Trichome density", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
       #fill=list(col=grey(c(0.7,0.9))),
       #line=list(col=grey(c(0,0.5))),
       #points=list(cex=1.5,col=grey(c(0.2,0.8)))
       ) 


```


## Plasticity overview {.tabset}

### SLA

```{r}
#read in emmeans. using lsmeans because its easier to see the graph
LSmeans_SLA <- read.csv("LSmeans_SLA_2.csv", stringsAsFactors=TRUE)

SLA <- lm(emmean ~ treatment*mat_treat, data = LSmeans_SLA)
Anova (SLA)

##use this

visreg(SLA, overlay = TRUE, "mat_treat", by="treatment", type="conditional", scale = "response", 
       xlab="Maternal environment", ylab="Specific leaf are", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
       fill=list(col=grey(c(0.7,0.9))),
       line=list(col=grey(c(0,0.5))),
       points=list(cex=1.5,col=grey(c(0.2,0.8))))  


#plasticity figure
ggplot(
  #subset(
    LSmeans_SLA,
   # treatment == "Herbivorized"),
  aes(x=treatment, y=emmean, color = genotype)) + # Change fill to color
  theme_classic(base_size = 22) + 
  #geom_point() + 
  stat_summary(fun=mean, position = "dodge") + 
  #stat_summary(
  #  geom="errorbar", 
  #  fun.data= mean_cl_boot,
  #  width = 0.1, size = 0.2, col = "grey57"
  #  ) + 
  # Lines by species using grouping
  #scale_color_viridis(discrete = FALSE) +
  #scale_fill_manual(values = cbp2)+
  stat_summary(aes(group = genotype), geom = "line", size=1.5, fun = mean) +
  ylab("Specific Leaf Area") +
  xlab("Treatment")

#plasticity figure
ggplot(
  subset(
    LSmeans_SLA,
   treatment == "Herbivorized"),
  aes(x=mat_treat, y=emmean, color = genotype)) + # Change fill to color
  theme_classic(base_size = 22) + 
  #geom_point() + 
  stat_summary(fun=mean, position = "dodge") + 
  #stat_summary(
  #  geom="errorbar", 
  #  fun.data= mean_cl_boot,
  #  width = 0.1, size = 0.2, col = "grey57"
  #  ) + 
  # Lines by species using grouping
  #scale_color_viridis(discrete = FALSE) +
  #scale_fill_manual(values = cbp2)+
  stat_summary(aes(group = genotype), geom = "line", size=1.5, fun = mean) +
  ylab("Specific Leaf Area") +
  xlab("Maternal enviornment")

#plasticity figure
ggplot(
  subset(
    LSmeans_SLA,
   treatment == "Control"),
  aes(x=mat_treat, y=emmean, color = genotype)) + # Change fill to color
  theme_classic(base_size = 22) + 
  #geom_point() + 
  stat_summary(fun=mean, position = "dodge") + 
  #stat_summary(
  #  geom="errorbar", 
  #  fun.data= mean_cl_boot,
  #  width = 0.1, size = 0.2, col = "grey57"
  #  ) + 
  # Lines by species using grouping
  #scale_color_viridis(discrete = FALSE) +
  #scale_fill_manual(values = cbp2)+
  stat_summary(aes(group = genotype), geom = "line", size=1.5, fun = mean) +
  ylab("Specific Leaf Area") +
  xlab("Maternal enviornment")


```






### Trichome Density

```{r}
#read in emmeans. using lsmeans because its easier to see the graph
LSmeans_tri <- read.csv("LSmeans_tri.csv", stringsAsFactors=TRUE)

TRI <- glm(emmean ~ treatment*mat_treat, data = LSmeans_tri)
Anova (TRI)

##use this

visreg(TRI, overlay = TRUE, "mat_treat", by="treatment", type="conditional", scale = "response", 
       xlab="Maternal environment", ylab="Trichome Density", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
       fill=list(col=grey(c(0.7,0.9))),
       line=list(col=grey(c(0,0.5))),
       points=list(cex=1.5,col=grey(c(0.2,0.8))))  

#plasticity figure
ggplot(
  #subset(
    LSmeans_tri,
   # treatment == "Herbivorized"),
  aes(x=treatment, y=emmean, color = genotype)) + # Change fill to color
  theme_classic(base_size = 22) + 
  #geom_point() + 
  stat_summary(fun=mean, position = "dodge") + 
  #stat_summary(
  #  geom="errorbar", 
  #  fun.data= mean_cl_boot,
  #  width = 0.1, size = 0.2, col = "grey57"
  #  ) + 
  # Lines by species using grouping
  #scale_color_viridis(discrete = FALSE) +
  #scale_fill_manual(values = cbp2)+
  stat_summary(aes(group = genotype), geom = "line", size=1.5, fun = mean) +
  ylab("Trichome Density") +
  xlab("Treatment")

#plasticity figure
ggplot(
  subset(
    LSmeans_tri,
   treatment == "Herbivorized"),
  aes(x=mat_treat, y=emmean, color = genotype)) + # Change fill to color
  theme_classic(base_size = 22) + 
  #geom_point() + 
  stat_summary(fun=mean, position = "dodge") + 
  #stat_summary(
  #  geom="errorbar", 
  #  fun.data= mean_cl_boot,
  #  width = 0.1, size = 0.2, col = "grey57"
  #  ) + 
  # Lines by species using grouping
  #scale_color_viridis(discrete = FALSE) +
  #scale_fill_manual(values = cbp2)+
  stat_summary(aes(group = genotype), geom = "line", size=1.5, fun = mean) +
  ylab("Trichome Density") +
  xlab("Maternal enviornment")

#plasticity figure
ggplot(
  subset(
    LSmeans_tri,
   treatment == "Control"),
  aes(x=mat_treat, y=emmean, color = genotype)) + # Change fill to color
  theme_classic(base_size = 22) + 
  #geom_point() + 
  stat_summary(fun=mean, position = "dodge") + 
  #stat_summary(
  #  geom="errorbar", 
  #  fun.data= mean_cl_boot,
  #  width = 0.1, size = 0.2, col = "grey57"
  #  ) + 
  # Lines by species using grouping
  #scale_color_viridis(discrete = FALSE) +
  #scale_fill_manual(values = cbp2)+
  stat_summary(aes(group = genotype), geom = "line", size=1.5, fun = mean) +
  ylab("Trichome Density") +
  xlab("Maternal enviornment")


```






## Fitness models: Fitness ~ garden x treatment x elev {.tabset)

# Probability of reproduction 

Individual 
```{r}

#looking at overall flowered
mod_flower<- glmer(Overall_flowered~ elev*treatment*mat_treat+ S_init_size + (1|block)+(1|genotype), data = gh2, control=glmerControl(optimizer="optimx", tolPwrss=1e-3, optCtrl=list(method="nlminb")), family=binomial)

Anova(mod_flower) # all seperate factors are sig, sig interaction btw mat_treat and elev
plot (mod_flower) #plot is strange, not sure if ok fit


flower <-predictorEffect("elev",  partial.residuals=TRUE, mod_flower)
plot(flower, lwd=2,xlab="Source Elevation (KM)", ylab="Probability of reproduction", pch=19, type="response",lines=list(multiline=TRUE, lty=2:1, col="black"), 
          partial.residuals=list(smooth=TRUE, pch=19, col="black"), ylim=c(0,1))

flower <-predictorEffect("elev",  partial.residuals=TRUE, mod_flower)
plot(flower, lwd=2,xlab="Source Elevation (KM)", ylab="Probability of reproduction", pch=19, type="response",lines=list(multiline=FALSE, lty=2:1, col="black"), 
          partial.residuals=list(smooth=TRUE, pch=19, col="black"), ylim=c(0,1))

#no parents
mod_pr1<- glmer(Overall_flowered~ elev*treatment*mat_treat+ S_init_size+(1|block)+(1|genotype), data =subset(gh2, mat_treat!="Parent"), control=glmerControl(optimizer="optimx", tolPwrss=1e-3,optCtrl=list(method="nlminb")), family=binomial)

Anova(mod_pr1)

flowerP <-predictorEffect("elev",  partial.residuals=TRUE, mod_pr1)

plot(flowerP, lwd=2,xlab="Source Elevation (KM)", ylab="Probability of reproduction", pch=19, type="response",lines=list(multiline=TRUE, lty=2:1,
                                                                              col="black"), partial.residuals=list(smooth=FALSE, pch=19, col="black"), ylim=c(0,1))

flowerP <-predictorEffect("elev",  partial.residuals=TRUE, mod_pr1)

plot(flowerP, lwd=2,xlab="Source Elevation (KM)", ylab="Probability of reproduction", pch=19, type="response",lines=list(multiline=FALSE, #lty=2:1,
                                                                              col="black"), partial.residuals=list(smooth=FALSE, pch=19, col="black"), ylim=c(0,1))


```

family level (not working)
```{r eval = FALSE, echo = FALSE}
# not printed
#lsmeans for prob flowering #not working, is resulting in negative emmean values

modB<- glmer(flowered~ genotype*mat_treat*treatment+ (1|block), data = gh2, control=glmerControl(optimizer="optimx", tolPwrss=1e-3, optCtrl=list(method="nlminb")), family=binomial)
Anova(modB,type="III")

fam_avg_linear<-emmeans(modB, ~genotype:mat_treat:treatment)
fam_means_linear<-as.data.frame(fam_avg_linear)

write.csv(fam_means_linear,file="LSmeans_flowered.csv")
LSmeans_flowered <- read.csv("LSmeans_flowered.csv", stringsAsFactors=TRUE)

#now we have lsmeans, but need to add corresponding elevation
elev <- gh2[c("genotype","elevation")] #make dataframe of genotypes and corresponding elev
elev <- unique(elev) #calls unique rows 
LSmeans_flowered <- merge(LSmeans_flowered,elev,by="genotype") #merge the dataframes

LSmeans_flowered$elev<-LSmeans_flowered$elevation/1000

write.csv(LSmeans_flowered,file="LSmeans_flw.csv")

LSmeans_flowered <- read.csv("LSmeans_flw.csv", stringsAsFactors=TRUE)

mod_pr<- glmer(emmean~ elev*mat_treat+treatment+ (1|genotype), data = LSmeans_flowered, control=glmerControl(optimizer="optimx", tolPwrss=1e-3, optCtrl=list(method="nlminb")), family=binomial)
Anova(mod_pr,type="III") #not working, error for negative emmean values

```


# Probability of survival

individual
```{r}
mod_surv<- glmer(S2_survival~elev*treatment*mat_treat + (1|block)+(1|genotype), data = gh2, control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e7)), family=binomial)
Anova(mod_surv) #only treatment is sig
plot(mod_surv)

survived <-predictorEffect("elev",  partial.residuals=FALSE, mod_surv)
plot(survived, lwd=2,xlab="Elevation of origin", ylab="Fitness (survival)", pch=19, type="response",lines=list(multiline=TRUE, lty=3:1, col="black"), 
          partial.residuals=list(smooth=FALSE, pch=19, col="black"), ylim=c(0,1))

```

family level not working
```{r eval = FALSE, echo = FALSE}
# not printed
#lsmeans for prob flowering #not working, is resulting in negative emmean values

mod_s<- glmer(survival~genotype*treatment*mat_treat + (1|block)+(1|genotype), data = gh2, control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e7)), family=binomial)
Anova(mod_s,type="III")

fam_avg_linear<-emmeans(mod_s, ~genotype:mat_treat:treatment)
fam_means_linear<-as.data.frame(fam_avg_linear)

write.csv(fam_means_linear,file="LSmeans_surv.csv")
LSmeans_surv <- read.csv("LSmeans_surv.csv", stringsAsFactors=TRUE)

#now we have lsmeans, but need to add corresponding elevation
elev <- gh2[c("genotype","elevation")] #make dataframe of genotypes and corresponding elev
elev <- unique(elev) #calls unique rows 
LSmeans_surv <- merge(LSmeans_surv,elev,by="genotype") #merge the dataframes

LSmeans_surv$elev<-LSmeans_surv$elevation/1000

write.csv(LSmeans_surv,file="LSmeans_surv.csv")

LSmeans_surv <- read.csv("LSmeans_surv.csv", stringsAsFactors=TRUE)

#em_surv<- glmer(emmean~ elev*mat_treat+treatment+ (1|genotype), data = LSmeans_surv, control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e7)), family=binomial)
#Anova(mod_pr,type="III") #not working, error for negative emmean values

```


# Fecundity 
individual
```{r}
#library(glmmTMB)

#looking at overall

#hurdle <- glmmTMB (Overall_Mature_silique_number ~ treatment*mat_treat*elev+S_init_size  + (1| block)+(1|genotype), zi=~ treatment*mat_treat*elev+S_init_size  + (1| block)+(1|genotype),data = gh2 ,family=truncated_nbinom2)

diagnose(hurdle)

Anova(hurdle,type="III", component="zi")

summary(hurdle) #zero inflated model is significant, but not sure if i am plotting it?


fruit <-predictorEffect("elev",  partial.residuals=TRUE, hurdle,component="zi")

plot(fruit, lwd=2,xlab="Source Elevation (KM)", ylab="Fruit", pch=19, type="response",lines=list(multiline=FALSE, #lty=2:1,
                                                                                                 col="black"), partial.residuals=list(smooth=FALSE, pch=19, col="black"), ylim=c(0,25))

plot(fruit, lwd=2,xlab="Source Elevation (KM)", ylab="Fruit", pch=19, type="response",lines=list(multiline=TRUE, lty=2:1, col="black"), partial.residuals=list(smooth=FALSE, pch=19, col="black"), ylim=c(0,25))

```

```{r}
#library(glmmTMB)

#looking at season 2 silique length

#nothing is significant here..

#hurdle2 <- glmmTMB (S2_Mature_length_siliques ~ treatment*mat_treat*elev+S_init_size  + (1| block)+(1|genotype), zi=~ treatment*mat_treat*elev+S_init_size  + (1| block)+(1|genotype),data = gh2 ,family=truncated_nbinom2)

diagnose(hurdle2)

Anova(hurdle2,type="III", component="zi")

summary(hurdle2)


fruit2 <-predictorEffect("elev",  partial.residuals=TRUE, hurdle2,component="zi")

plot(fruit2, lwd=2,xlab="Source Elevation (KM)", ylab="Fruit", pch=19, type="response",lines=list(multiline=FALSE, #lty=2:1,
                                                                                                 col="black"), partial.residuals=list(smooth=FALSE, pch=19, col="black"), ylim=c(0,500))

plot(fruit2, lwd=2,xlab="Source Elevation (KM)", ylab="Fruit", pch=19, type="response",lines=list(multiline=TRUE, lty=2:1, col="black"), partial.residuals=list(smooth=FALSE, pch=19, col="black"), ylim=c(0,500))

#no parents


#hurdle3 <- glmmTMB (S2_Mature_length_siliques ~ treatment*mat_treat*elev+S_init_size  + (1| block)+(1|genotype), zi=~ treatment*mat_treat*elev+S_init_size  + (1| block)+(1|genotype),data = subset(gh2, mat_treat!= "Parent") ,family=truncated_nbinom2)

diagnose(hurdle3)

Anova(hurdle3,type="III", component="zi")

summary(hurdle3)


fruit3 <-predictorEffect("elev",  partial.residuals=TRUE, hurdle3,component="zi")

plot(fruit3, lwd=2,xlab="Source Elevation (KM)", ylab="Fruit", pch=19, type="response",lines=list(multiline=FALSE, #lty=2:1,
                                                                                                 col="black"), partial.residuals=list(smooth=FALSE, pch=19, col="black"), ylim=c(0,500))

plot(fruit3, lwd=2,xlab="Source Elevation (KM)", ylab="Fruit", pch=19, type="response",lines=list(multiline=TRUE, lty=2:1, col="black"), partial.residuals=list(smooth=FALSE, pch=19, col="black"), ylim=c(0,500))


```


Family level
```{r eval = FALSE, echo = FALSE}
# not printed
#calculated family-level means. To do so, for each relevant unit (genotype or maternal id), calculate the total number of individuals planted, the total number of individuals that reproduced, and then silique production amongst those that reproduced. From the family level data, you can calculate fitness as: (# of individuals that reproduced / # of individuals planted) * silique production amongst those that reproduced

#to make the emmeans file

reproduced <- subset(gh2,flowered == "1")
reproduced <- subset(reproduced, Mature_silique_number!="0")


modF<- lmer( Mature_silique_number ~ genotype*mat_treat*treatment +(1|block),control = lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e7)), data = reproduced)
fam_avg_linear<-emmeans(modF, ~genotype:mat_treat:treatment)
fam_means_linear<-as.data.frame(fam_avg_linear, type = "response")
summary(fam_avg_linear, type = "response")
write.csv(fam_means_linear,file="LSmeans_fruit.csv")

#read in emmeans
LSmeans_fruit <- read.csv("LSmeans_fruit.csv", stringsAsFactors=TRUE)

#now we have lsmeans, but need to add corresponding elevation
elev <- gh2[c("genotype","elevation")] #make dataframe of genotypes and corresponding elev
elev <- unique(elev) #calls unique rows 
LSmeans_fruit <- merge(LSmeans_fruit,elev,by="genotype") #merge the dataframes

LSmeans_fruit$elev<-LSmeans_fruit$elevation/1000
#LSmeans_SLA$emmean<-LSmeans_SLA$emmean*100

write.csv(LSmeans_fruit,file="LSmeans_fruit.csv")

```



## LAR {.tabset}

individual 
```{r}
#have to curate the dataset to focus on herb treatment and remove NAs
#LAR 3 has the most damage, LAR 13 is the most recent

LAR_data <- subset(gh2, treatment == "Herbivorized")

LAR_3 <- drop_na(LAR_data,LAR_prop2) #this removes the rows without LAR values
LAR_3 <- dplyr::select(LAR_3, LAR_prop2, elev, genotype, treatment, mat_treat, exp_ID, S_init_size, block)

#response variable cant have zeros, so I added 0.0001 to every value

LAR_3$LAR_prop2 <- LAR_3$LAR_prop2 + 0.0001
gamlss_mod1<- gamlss (formula=LAR_prop2~elev*mat_treat+ S_init_size+ random(block)+random(genotype), family=BE, data= LAR_3)
summary(gamlss_mod1)
plot(gamlss_mod1)


LAR_13 <- drop_na(LAR_data,LAR_prop13) #this removes the rows without LAR values
LAR_13 <- dplyr::select(LAR_13, LAR_prop13, elev, genotype, treatment, mat_treat, exp_ID, S_init_size, block)

gamlss_mod2<- gamlss (formula=LAR_prop13~elev*mat_treat+ random(block)+random(genotype), family=BEZI, data= LAR_13)
summary(gamlss_mod2)
plot(gamlss_mod2)

visreg(gamlss_mod1, 'elev', by= "mat_treat", overlay = FALSE, type="conditional", 
       #scale = "response", 
       xlab="Elevation (m)", ylab="Percentage leaf area herbivorized", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
       fill=list(col="blue"),
       line=list(col=grey(c(0,0.8))),
       points=list(cex=1.5,col=grey(c(0,0.8)))) 

visreg(gamlss_mod2, 'elev', by= "mat_treat", overlay = FALSE, type="conditional", 
       #scale = "response", 
       xlab="Elevation (m)", ylab="Percentage leaf area herbivorized", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
       fill=list(col="blue"),
       line=list(col=grey(c(0,0.8))),
       points=list(cex=1.5,col=grey(c(0,0.8)))) 

#lmer model
  modA<- lmer(LAR_prop2~ mat_treat*elev+ S_init_size+ (1|block)+(1|genotype),data= LAR_3)
 Anova(modA,type="III")
 ##You can see here that the residuals aren't great
 plot(modA)
 
 visreg(modA, 'elev', by= "mat_treat", overlay = FALSE, type="conditional", 
       #scale = "response", 
       xlab="Elevation (m)", ylab="Percentage leaf area herbivorized", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
       fill=list(col="blue"),
       line=list(col=grey(c(0,0.8))),
       points=list(cex=1.5,col=grey(c(0,0.8)))) 
 



``` 

