---
title: "Herbivory_prelim"
output: html_document
date: "2023-09-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
# read in some libraries
library(lme4) #for running linear mixed models
#library(lmerTest)
#library(broom)
library(ggplot2) #for plotting 
#library(bootpredictlme4)
library(visreg) # for plotting
library(car) # to run ANOVA on model output
#library(MuMIn)
library(plyr) # for data wrangling
library(dplyr) # for data wrangling
#library(mgcv)
#library(survival)
library(coxme)
#library(survminer)
library(effects) # for plotting
library(emmeans)
#library(optimx)


```

setwd("/Users/inam/Library/CloudStorage/OneDrive-UniversityofGeorgia/Inam_experiments/Herbivory_data/field/2023_files/census_files")
setwd("/Users/inam/OneDrive - University of Georgia/Inam_experiments/Herbivory_data/field/2023_files/census_files")

## Schofield
```{r, include = FALSE}
#### read in data ####

setwd("/Users/inam/OneDrive - University of Georgia/Inam_experiments/Herbivory_data/field/2023_files/census_files")
data<- read.csv("inam_schofield_092623.csv")

#data<- filter(data,include == "1")


data $S_elev<-scale(data$Elevation,center=TRUE, scale=TRUE)
data $elev_km<-data$Elevation/1000
data $init_size<-scale(data$initial_size,center=TRUE, scale=TRUE)


data$Genotype<-as.factor(data$Genotype)
data$treatment<-as.factor(data$treatment)
data$Block<-as.factor(data$Block)
data$cohort<-as.factor(data$cohort)

data$elev_dist<-data$Elevation-3133

#data$elev_dist<- abs(data$elev_dist)
data$abs_elev_dist<- abs(data$elev_dist)

data $S_elev_dist_abs<-scale(data$abs_elev_dist,center=TRUE, scale=TRUE) #needed to be scaled to avoid issues in model

data$elev_dist_km<- data$elev_dist/1000
data $S_elev_dist<-scale(data$elev_dist,center=TRUE, scale=TRUE)

#concatenate garden and treatment to plot from visreg
#data $garden_treat<-interaction(data $garden, data $treatment,sep = "_")

#Let's concatenate block and garden so that we don't have to worry about nesting block within garden

#data $block_garden<-interaction(data $block, data $garden,sep = "_")

#census 2 and 4 have the damage census

census2 <- filter(data, Census == "2")
census4 <- filter(data, Census == "4") #incomplete census

#census 7 is final census
census7 <- filter(data, Census == "7")

```

### survival, reproduction, fecundity

```{r}

#survival

mod_surv<- glmer(Survival~elev_km*treatment + cohort+init_size+ (1|Block)+(1|Genotype), data = census7, control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e7)), family=binomial) #when i add cohort to the model, it doesnt work.. 
Anova(mod_surv)
plot(mod_surv)

#no residuals, multiline
survived <-predictorEffect("elev_km",  partial.residuals=FALSE, mod_surv)
plot(survived, lwd=2,xlab="Source elevation (Km)", ylab="Fitness (survival)", pch=19, type="response",lines=list(multiline=TRUE, lty=3:1, col="black"), 
     partial.residuals=list(smooth=TRUE, pch=19, col="black"), ylim=c(0,1))


#residuals
survived <-predictorEffect("elev_km",  partial.residuals=TRUE, mod_surv)
plot(survived, lwd=2,xlab="Elevation of origin", ylab="Fitness (survival)", pch=19, type="response",lines=list(multiline=FALSE, lty=3:1, col="black"), 
     partial.residuals=list(smooth=TRUE, pch=19, col="black"), ylim=c(0,1))



mod_2<- glmer(survival~garden_treat*elev_km+ (1|block)+(1|Genotype), data = data, control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e7)), family=binomial) #best model, but still nothing
Anova(mod_2) 

#no residuals, multiline

visreg(mod_2, overlay = FALSE, "elev_km", by="garden_treat", type="conditional", scale = "response", 
       xlab="Source elevation (Km)", ylab="Fitness (Prob Survival)", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
       fill=list(col="blue"),
       #line=list(col=grey(c(0,0.8))),
       #points=list(cex=1.5,col=grey(c(0,0.8))),
       jitter = TRUE)





#prob reproduction

mod_reproduction<- glmer(Reproduction~treatment*elev_km+ cohort+init_size+(1|Block)+(1|Genotype), data = census7, control=glmerControl(optimizer="optimx", tolPwrss=1e-3, optCtrl=list(method="nlminb")), family=binomial)
Anova(mod_reproduction,type="III")  #significance of garden
plot(mod_reproduction)

visreg(mod_reproduction, overlay = TRUE, "elev_km", by="treatment", type="conditional", scale = "response", 
       xlab="Source Elevation (Km)", ylab="Fitness (Prob Flowering)", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
       fill=list(col="blue"),
       line=list(col=grey(c(0,0.8))),
       points=list(cex=1.5,col=grey(c(0,0.8))),
       jitter = TRUE)
       

reproduction <-predictorEffect("elev_km",  partial.residuals=TRUE, mod_reproduction)
plot(reproduction, lwd=2,xlab="Elevation of origin", ylab="Fitness (Prob Reproduction)", pch=19, type="response",lines=list(multiline=FALSE, lty=3:1, col="black"), 
     partial.residuals=list(smooth=TRUE, pch=19, col="black"), ylim=c(0,1))

#subset only surviving plants

surv <- subset(census7, Survival=="1")
surv2022 <- subset(census7, cohort=="2022")


mod_reproduction1<- glmer(Reproduction~treatment*elev_km+init_size (1|Block)+(1|Genotype), data = surv2022, control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e7)), family=binomial)
Anova(mod_reproduction1,type="III")  
plot(mod_reproduction1)

visreg(mod_reproduction1, overlay = TRUE, "cohort", type="conditional", scale = "response", 
       xlab="Source Elevation (Km)", ylab="Fitness (Prob Flowering)", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
       fill=list(col="blue"),
       line=list(col=grey(c(0,0.8))),
       points=list(cex=1.5,col=grey(c(0,0.8))),
       jitter = TRUE)



reproduction <-predictorEffect("elev_km",  partial.residuals=TRUE, mod_reproduction1)
plot(reproduction, lwd=2,xlab="Elevation of origin", ylab="Fitness (reproduction)", pch=19, type="response",lines=list(multiline=TRUE, lty=2:1, col="black"), 
     partial.residuals=list(smooth=TRUE
```

### LA models

```{r}
##Then, we examine local adaptation using the probability of flowering as the fitness component. Here, values of 0 include individuals that failed to flower along with those that died

mod_repro<- glmer(Reproduction~treatment* elev_dist_km+I(elev_dist_km^2)*treatment +(1|Block)+(1|Genotype), data = census7, control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e7)), family=binomial) 

Anova(mod_repro)

pred_repro <-predictorEffect("elev_dist_km",  partial.residuals=FALSE, mod_repro)

plot(pred_repro, lwd=2,xlab="Elevational transfer distance", ylab="Fitness (probability of flowering)", pch=19, type="response",lines=list(multiline=FALSE, lty=2:1, col="black"), 
     
     partial.residuals=list(smooth=FALSE, pch=19, col="black"))

#model for RMBL talk
visreg(mod_repro, overlay = FALSE, "elev_dist_km", by="treatment", type="contrast", 
       scale = "response",
       xlab="Elevational transfer distance", ylab="Fitness (probability of flowering)", partial=TRUE,
       fill=list(col="light grey"
                 #(c(0.99), alpha=0)
       ), band = FALSE,
       line=list(col=grey(c(0.2,0.6))),
       points=list(cex=0.65,  pch=(19)))



#survival

mod_surv<- glmer(Survival~treatment* elev_dist_km+I(elev_dist_km^2)*treatment +cohort+(1|Block)+(1|Genotype), data = census7, control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e7)), family=binomial) 

Anova(mod_surv)

mod_surv1 <-predictorEffect("elev_dist_km",  partial.residuals=TRUE, mod_surv)

plot(mod_surv1, lwd=2,xlab="Elevational transfer distance", ylab="Fitness (probability of survival)", pch=19, type="response",lines=list(multiline=TRUE, lty=2:1, col="black"), 
     
     partial.residuals=list(smooth=TRUE, pch=19, col="black"))


#model for RMBL talk
visreg(mod_surv, overlay = FALSE, "elev_dist_km", by="treatment", type="contrast", 
       scale = "response",
       xlab="Elevational transfer distance", ylab="Fitness (survival)", partial=TRUE,
       fill=list(col="light grey"
                 #(c(0.99), alpha=0)
       ), band = FALSE,
       line=list(col=grey(c(0.2,0.6))),
       points=list(cex=0.65,  pch=(19)))

```

### LAR for BT effectiveness

```{r}

#need to update with specific censuses
census2$LAR_prop<- census2$LAR/100

##Check that the conversion worked

hist(census2$LAR_prop)


#remove NA values for gamlss


data_LAR<-census2 %>% dplyr::select(treatment, S_elev, elev_km,Genotype,LAR_prop,Block)

data_LAR<-na.omit(data_LAR)


##Okay, it looks like there were no NAs in that column, so we can proceed to the zero-one inflated negative binomial regression. What I've written out here is the full model, which has convergence issues.

#LAR_prop~treatment*S_elev*garden+ random(block_garden)+random(genotype)
gamlss.modelA<- gamlss (formula=LAR_prop~treatment*S_elev+ random(Block)+random(Genotype), sigma.formula=LAR_prop~treatment*S_elev+ random(Block)+random(Genotype), nu.formula=LAR_prop~treatment*S_elev+ random(Block)+random(Genotype), tau.formula=LAR_prop~treatment*S_elev+ random(Block)+random(Genotype), family=BEINF, data= data_LAR)


##Perhaps we don't want to interact everything. Please keep in mind that garden should be a fixed effect, not random (you only have 2 gardens), but maybe the patterns don't differ much across gardens:



#LAR_prop~treatment*S_elev+garden+ random(block_garden)+random(genotype)
gamlss.model<- gamlss (formula=LAR_prop~treatment*S_elev+garden+ random(block_garden)+random(Genotype), sigma.formula=LAR_prop~treatment*S_elev+garden+ random(block_garden)+random(Genotype), nu.formula=LAR_prop~treatment*S_elev+garden+ random(block_garden)+random(Genotype), tau.formula=LAR_prop~treatment*S_elev+garden+ random(block_garden)+random(Genotype), family=BEINF, data= data_LAR)

#many many warnings

gamlss.modelA
plot(gamlss.modelA)
summary(gamlss.modelA) #nu only has garden as significant

#Stepwise analyis to find the best model (https://rdrr.io/cran/gamlss/man/stepGAIC.html). This process takes a couple of minutes.

dropterm(gamlss.modelA)
mod2<-stepGAIC(gamlss.modelA)
mod2$anova

summary(mod2) # there are significant effects of treatment, elevation of origin and their interaction for mu (the probability of being damaged). For nu (amount of damage on plants with >0 and <1 damage; i.e., the beta component), there is a significant effect of elevation of origin and garden, but not treatment or elevation by treatment). For tau (probability of 100% damage – which you likely don’t have), there are no significant effects.


#So, we might be able to remove the tau component from the model, and run a zero-inflated model:
  
  gamlss.modelB<- gamlss (formula=LAR_prop~treatment+S_elev+ random(Block)+random(Genotype), 
                          sigma.formula=LAR_prop~treatment+S_elev+ random(Block)+random(Genotype), 
                          nu.formula=LAR_prop~treatment+S_elev+ random(Block)+random(Genotype), family=BEINF, data= data_LAR)

plot(gamlss.modelB)

summary(gamlss.modelB)
  
  
visreg(gamlss.modelB, "treatment", type="conditional", #scale = "response", 
         xlab="Elev", ylab="LAR", partial=TRUE,
         fill=list(col="light grey"
                   #(c(0.99), alpha=0)
         ), band = FALSE,
         #line=list(col=grey(c(0.2,0.6))),
          points=list(cex=0.65,  pch=(19)))  

c2021 $garden_treat<-interaction(c2021 $treatment, c2021 $garden,sep = "_")
  
gamlss.modelE<- gamlss (formula=LAR_prop~S_elev+garden_treat + random(block_garden)+random(Genotype), sigma.formula=LAR_prop~S_elev+ garden_treat+ random(block_garden)+random(Genotype), nu.formula=LAR_prop~S_elev+ garden_treat+ random(block_garden)+random(Genotype), family=BEINF, data= data_LAR)
  
  plot(gamlss.modelE)
  
  summary(gamlss.modelE)
  
  visreg(gamlss.modelE, overlay = FALSE, "S_elev", by="garden_treat", type="conditional", 
         #scale = "response",   
         xlab="Source elevation", ylab="Leaf area removed", partial=TRUE,  band = FALSE)    


  #You can create a datafile with the predicted data from the nu component using this code for plotting:
  pred<-predict(gamlss.modelB, newdata=data_LAR, type="response", what="nu"
                )
  
  pred<-predict(gamlss.modelB, type="response", what="mu")
  data_LAR <- cbind(data_LAR,pred)

  data_LAR$LAR <- (data_LAR$pred*100)
  

ggplot(data_LAR, aes(x = elev_km, y = LAR, color = treatment))+
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(x = "Source elevation", y = "Leaf Area Removed", color = "treatment") + 
  theme_bw() + scale_color_manual(values=c("#009E73","#CC79A7"))

modB<- lmer (LAR_prop~elev_km*treatment+cohort+init_size+(1|Block),control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e7)), data=census2)
Anova(modB)
summary(modB)

plot(predictorEffects(modB, ~ elev_km), type="response",partial.residuals=TRUE, confint=list(style="auto"), xlab="Population source elevation (Km)", ylab="Leaf area herbivorized",line=list(multiline=TRUE, ylim(0,0.5),lty=1:2,col=c("#009E73","#CC79A7")))
```

## Gothic
```{r, include = FALSE}
#### read in data ####
data<- read.csv("inam_gothic_092623.csv")

#data<- filter(data,include == "1")


data $S_elev<-scale(data$Elevation,center=TRUE, scale=TRUE)
data $elev_km<-data$Elevation/1000
data $init_size<-scale(data$initial_size,center=TRUE, scale=TRUE)


data$Genotype<-as.factor(data$Genotype)
data$treatment<-as.factor(data$treatment)
data$Block<-as.factor(data$Block)
data$cohort<-as.factor(data$cohort)

data$elev_dist<-data$Elevation-2890

#data$elev_dist<- abs(data$elev_dist)
data$abs_elev_dist<- abs(data$elev_dist)

data $S_elev_dist_abs<-scale(data$abs_elev_dist,center=TRUE, scale=TRUE) #needed to be scaled to avoid issues in model

data$elev_dist_km<- data$elev_dist/1000
data $S_elev_dist<-scale(data$elev_dist,center=TRUE, scale=TRUE)

#concatenate garden and treatment to plot from visreg
#data $garden_treat<-interaction(data $garden, data $treatment,sep = "_")

#Let's concatenate block and garden so that we don't have to worry about nesting block within garden

#data $block_garden<-interaction(data $block, data $garden,sep = "_")

#census 3 7 8 have the damage census



census3 <- filter(data, Census == "3")
census7 <- filter(data, Census == "7") 
census8 <- filter(data, Census == "8") 

#census 11 is final census
census11 <- filter(data, Census == "11")

```

### survival, reproduction, fecundity

```{r}

#survival

mod_surv<- glmer(Survival~elev_km*treatment + cohort+init_size+ (1|Block)+(1|Genotype), data = census11, control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e7)), family=binomial) #when i add cohort to the model, it doesnt work.. 
Anova(mod_surv)
plot(mod_surv)

#no residuals, multiline
survived <-predictorEffect("elev_km",  partial.residuals=FALSE, mod_surv)
plot(survived, lwd=2,xlab="Source elevation (Km)", ylab="Fitness (survival)", pch=19, type="response",lines=list(multiline=TRUE, lty=3:1, col="black"), 
     partial.residuals=list(smooth=TRUE, pch=19, col="black"), ylim=c(0,.5))


#residuals
survived <-predictorEffect("elev_km",  partial.residuals=TRUE, mod_surv)
plot(survived, lwd=2,xlab="Elevation of origin", ylab="Fitness (survival)", pch=19, type="response",lines=list(multiline=FALSE, lty=3:1, col="black"), 
     partial.residuals=list(smooth=TRUE, pch=19, col="black"), ylim=c(0,1))


#prob reproduction

mod_reproduction<- glmer(Reproduction~treatment*elev_km+ cohort+init_size+(1|Block)+(1|Genotype), data = census11, control=glmerControl(optimizer="optimx", tolPwrss=1e-3, optCtrl=list(method="nlminb")), family=binomial)
Anova(mod_reproduction,type="III")
plot(mod_reproduction)

visreg(mod_reproduction, overlay = TRUE, "elev_km", by="treatment", type="conditional", scale = "response", 
       xlab="Source Elevation (Km)", ylab="Fitness (Prob Flowering)", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
       fill=list(col="blue"),
       line=list(col=grey(c(0,0.8))),
       points=list(cex=1.5,col=grey(c(0,0.8))),
       jitter = TRUE)
       

reproduction <-predictorEffect("elev_km",  partial.residuals=TRUE, mod_reproduction)
plot(reproduction, lwd=2,xlab="Elevation of origin", ylab="Fitness (Prob Reproduction)", pch=19, type="response",lines=list(multiline=FALSE, lty=3:1, col="black"), 
     partial.residuals=list(smooth=TRUE, pch=19, col="black"), ylim=c(0,1))

#subset only surviving plants

surv <- subset(census11, Survival=="1")
surv2022 <- subset(census11, cohort=="2022")


mod_reproduction1<- glmer(Reproduction~treatment*elev_km+init_size+cohort +(1|Block)+(1|Genotype), data = surv, control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e7)), family=binomial)
Anova(mod_reproduction1,type="III")  
plot(mod_reproduction1)

visreg(mod_reproduction1, overlay = TRUE, "elev_km", type="conditional", scale = "response", 
       xlab="Source Elevation (Km)", ylab="Fitness (Prob Flowering)", partial=TRUE, cex.lab = 1.5,cex.axis = 1.5,
       fill=list(col="blue"),
       line=list(col=grey(c(0,0.8))),
       points=list(cex=1.5,col=grey(c(0,0.8))),
       jitter = TRUE)



reproduction <-predictorEffect("elev_km",  partial.residuals=TRUE, mod_reproduction1)
plot(reproduction, lwd=2,xlab="Elevation of origin", ylab="Fitness (reproduction)", pch=19, type="response",lines=list(multiline=TRUE, lty=2:1, col="black"), 
     partial.residuals=list(smooth=TRUE
```

### LA models

```{r}
##Then, we examine local adaptation using the probability of flowering as the fitness component. Here, values of 0 include individuals that failed to flower along with those that died

mod_repro<- glmer(Reproduction~treatment* elev_dist_km+I(elev_dist_km^2)*treatment+cohort+init_size +(1|Block)+(1|Genotype), data = census11, control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e7)), family=binomial) 

Anova(mod_repro)

pred_repro <-predictorEffect("elev_dist_km",  partial.residuals=FALSE, mod_repro)

plot(pred_repro, lwd=2,xlab="Elevational transfer distance", ylab="Fitness (probability of flowering)", pch=19, type="response",lines=list(multiline=FALSE, lty=2:1, col="black"), 
     
     partial.residuals=list(smooth=FALSE, pch=19, col="black"))

#model for RMBL talk
visreg(mod_repro, overlay = FALSE, "elev_dist_km", by="treatment", type="contrast", 
       scale = "response",
       xlab="Elevational transfer distance", ylab="Fitness (probability of flowering)", partial=TRUE,
       fill=list(col="light grey"
                 #(c(0.99), alpha=0)
       ), band = FALSE,
       line=list(col=grey(c(0.2,0.6))),
       points=list(cex=0.65,  pch=(19)))



#survival

mod_surv<- glmer(Survival~treatment* elev_dist_km+I(elev_dist_km^2)*treatment +init_size+(1|Block)+(1|Genotype), data = census11, control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e7)), family=binomial) 

Anova(mod_surv)

mod_surv1 <-predictorEffect("elev_dist_km",  partial.residuals=TRUE, mod_surv)

plot(mod_surv1, lwd=2,xlab="Elevational transfer distance", ylab="Fitness (probability of survival)", pch=19, type="response",lines=list(multiline=TRUE, lty=2:1, col="black"), 
     
     partial.residuals=list(smooth=FALSE, pch=19, col="black"))


plot(predictorEffects(mod_surv, ~ elev_dist_km), type="response",partial.residuals=TRUE, confint=list(style="auto"), xlab="Elevational transfer distance (Km)", ylab="Fitness (Probability of survival)",line=list(multiline=TRUE, lty=1:2,col=c("#009E73","#CC79A7")))

```

### LAR for BT effectiveness

```{r}

#need to update with specific censuses
census8$LAR_prop<- census8$LAR/100
census7$LAR_prop<- census7$LAR/100
census3$LAR_prop<- census3$LAR/100

##Check that the conversion worked

hist(census8$LAR_prop)


#remove NA values for gamlss


data_LAR<-census3 %>% dplyr::select(treatment, S_elev, elev_km,Genotype,LAR_prop,Block)

data_LAR<-na.omit(data_LAR)


##Okay, it looks like there were no NAs in that column, so we can proceed to the zero-one inflated negative binomial regression. What I've written out here is the full model, which has convergence issues.

#LAR_prop~treatment*S_elev*garden+ random(block_garden)+random(genotype)
gamlss.modelA<- gamlss (formula=LAR_prop~treatment*S_elev+ random(Block)+random(Genotype), sigma.formula=LAR_prop~treatment*S_elev+ random(Block)+random(Genotype), nu.formula=LAR_prop~treatment*S_elev+ random(Block)+random(Genotype), tau.formula=LAR_prop~treatment*S_elev+ random(Block)+random(Genotype), family=BEINF, data= data_LAR)


#many many warnings
gamlss.modelA
plot(gamlss.modelA)
summary(gamlss.modelA) #nu only has garden as significant

#Stepwise analyis to find the best model (https://rdrr.io/cran/gamlss/man/stepGAIC.html). This process takes a couple of minutes.

dropterm(gamlss.modelA)
mod2<-stepGAIC(gamlss.modelA)
mod2$anova

summary(mod2) 

#


#So, we might be able to remove the tau component from the model, and run a zero-inflated model:
  
  gamlss.modelB<- gamlss (formula=LAR_prop~treatment+S_elev+ random(Block)+random(Genotype), 
                          sigma.formula=LAR_prop~treatment+S_elev+ random(Block)+random(Genotype), 
                          nu.formula=LAR_prop~treatment+S_elev+ random(Block)+random(Genotype), family=BEINF, data= data_LAR)

plot(gamlss.modelB)

summary(gamlss.modelB)
  
  
visreg(gamlss.modelB, "treatment", type="conditional", #scale = "response", 
         xlab="Elev", ylab="LAR", partial=TRUE,
         fill=list(col="light grey"
                   #(c(0.99), alpha=0)
         ), band = FALSE,
         #line=list(col=grey(c(0.2,0.6))),
          points=list(cex=0.65,  pch=(19)))  

c2021 $garden_treat<-interaction(c2021 $treatment, c2021 $garden,sep = "_")
  
gamlss.modelE<- gamlss (formula=LAR_prop~S_elev+garden_treat + random(block_garden)+random(Genotype), sigma.formula=LAR_prop~S_elev+ garden_treat+ random(block_garden)+random(Genotype), nu.formula=LAR_prop~S_elev+ garden_treat+ random(block_garden)+random(Genotype), family=BEINF, data= data_LAR)
  
  plot(gamlss.modelE)
  
  summary(gamlss.modelE)
  
  visreg(gamlss.modelE, overlay = FALSE, "S_elev", by="garden_treat", type="conditional", 
         #scale = "response",   
         xlab="Source elevation", ylab="Leaf area removed", partial=TRUE,  band = FALSE)    


  #You can create a datafile with the predicted data from the nu component using this code for plotting:
  pred<-predict(gamlss.modelB, newdata=data_LAR, type="response", what="nu"
                )
  
  pred<-predict(gamlss.modelB, type="response", what="mu")
  data_LAR <- cbind(data_LAR,pred)

  data_LAR$LAR <- (data_LAR$pred*100)
  

ggplot(data_LAR, aes(x = elev_km, y = LAR, color = treatment))+
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(x = "Source elevation", y = "Leaf Area Removed", color = "treatment") + 
  theme_bw() + scale_color_manual(values=c("#009E73","#CC79A7"))

modB<- lmer (LAR_prop~elev_km*treatment+cohort+init_size+(1|Block),control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e7)), data=census3)
Anova(modB)

visreg(modB,overlay=T,"elev_km", by ="treatment")
plot(predictorEffects(modB, ~ elev_km), type="response",partial.residuals=TRUE, confint=list(style="auto"), xlab="Population source elevation (Km)", ylab="Leaf area herbivorized",line=list(multiline=TRUE, lty=1:2,col=c("#009E73","#CC79A7")))

```